An Empirical Analysis of the Role of Energy in Economic Growth

### 2013-05-24 EconGrowth.Rnw
Improved spacing in a bullet list.

The following tables show covariances among GDP ($y$) and factors of production ($k$, $l$, $q$, $x$, and $u$). Covariances are calculated for the following years: 
\begin{itemize}
  \item{1980-2011 for covariances among $y$, $k$, $l$, $q$, and $x$ for\\*developed economies;}
  \item{1980-2000 for covariances involving $u$ for developed economies; and}
  \item{1991-2011 for covariances among $y$, $k$, $l$, $q$, and $x$ for\\*developing economies.}
\end{itemize}

>>>>

The following tables show covariances among GDP ($y$) and factors of production ($k$, $l$, $q$, $x$, and $u$). Covariances are calculated for the following years: 
\begin{itemize}
  \item{1980-2011 for covariances among $y$, $k$, $l$, $q$, and $x$ for developed\\*economies;}
  \item{1980-2000 for covariances involving $u$ for developed economies; and}
  \item{1991-2011 for covariances among $y$, $k$, $l$, $q$, and $x$ for developing\\*economies.}
\end{itemize}
